Extending the WebID Protocol with Access Delegation

### 2012-08-04 paper.tex
shorted code and improved merges

\lstinputlisting[
    lastline=26,name=webid,style=turtle,float=htb,label=listing:multipleKeyProfile,
    basicstyle=\ttfamily\scriptsize,
    caption={Profile allowing three different agents to act as Romeo}
]{Listings/mutlipleKeys.ttl}\todo{ST: Can we shorten this to two agents?}

@@

But when the origin server $OS$ is serving a number of different profiles $P_1 \ldots P_n$ each identifying the N users $U_1 \ldots U_n$ and is acting on behalf of a these users, as would be the case for a company, government agency, school, educational instituion, charyity, football club, ... server, then we have two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.

Things get more interesting when an origin server agent $A$ is serving a number of different profiles $P_1$, $P_2$, $P_3$, ... $P_n$ each identifying the N users $U_1$, $U_2$, $U_3$, ..., $U_n$ and is acting on behalf of a these users.
This would be the situation for servers acting for companies, government agencies, educational instituion, charities, football club, ....
This brings up two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.

@@

\lstinputlisting[
    lastline=36,name=views,style=turtle,float=htb,label=listing:views,
    basicstyle=\ttfamily\scriptsize,
    caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
]{Listings/views.n3}\todo{ST: \autoref{listing:views} is too long (maybe shorten, I dont know)}

@@

In order to reduce the number of open connections to any server down to a minimum, it would be useful if the origin server could identify itself directly when making a request and specify on behalf of which of its users it was acting on.
One way would be for the origin server acting as client to simply use the same public key as the origin server acting as server - that is it could use the same public key as the one used by the TLS server.
It could even use the same certificate.
This would make clear to any server it was connecting to, that it could rely on this server as much as it could on the identity of any resource, and in particular any WebID profils served by that server.

>>>>

\lstinputlisting[
    firstline=6,lastline=26,name=webid,style=turtle,float=htb,label=listing:multipleKeyProfile,
    basicstyle=\ttfamily\scriptsize,
    caption={Profile allowing three different agents to act as Romeo}
]{Listings/mutlipleKeys.ttl}

@@

Things get more interesting when an origin server agent $A$ is serving a number of different profiles $P_1$ \ldots $P_n$ each identifying the N users $U_1$ \ldots $U_n$ and is acting on behalf of a these users.
This would be the situation for servers acting for companies, government agencies, educational instituion, charities, football club, ....
This brings up two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.

@@

\lstinputlisting[
    firstline=8,lastline=36,name=views,style=turtle,float=htb,label=listing:views,
    basicstyle=\ttfamily\scriptsize,
    caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
]{Listings/views.n3}

@@

In order to reduce the number of open connections to any server down to a minimum, it would be useful if the origin server could identify itself directly when making a request and specify on behalf of which of its users it was acting on per request so as to be able to make multiple requests on the same TLS connection.
One way would be for the origin server acting as client to simply use the same public key as the origin server acting as server - that is it could use the same public key as the one used by the TLS server.
It could even use the same certificate.
This would make clear to any server it was connecting to, that it could rely on this server as much as it could on the identity of any resource, and in particular any WebID profils served by that server.
